---
title: "3C analysis"
author: "Winnie Zhuang"
date: "3/7/2022"
output: html_document
---
# Set Up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(car)
library(tidyverse)
library(corrplot)
library(PerformanceAnalytics)

```

##load in processed data file
```{r}
dt<-read_csv("omit_df.csv")
#make rownames
dt$rownames<-rownames(dt)
dt %>% select(rownames,id)
```

## load in variable key

# MCQ and general confidence about the future
Hypothesis: People who report less confidence about the future should report more temporal discounting. 
Measure and Items needed:
General Confidence Scale (Keller et., all 2011): GCS_1:6
MCQ

## Plots
```{r}
hist(dt$GCS_index)
hist(log(dt$MeanK))

plot(dt$GCS_index,log(dt$MeanK))
```
Hmm doesn't appear to be too much of a relationship. 

## Stats
```{r}
lm_mcq.gcf<-lm(log(dt$MeanK)~dt$GCS_index,data=dt)
summary(lm_mcq.gcf)

#plot 
ggplot(aes(x=GCS_index,y=log(MeanK)),data=dt)+
  geom_point() +
  geom_smooth(method="lm")
```
A trending negative relationship. Higher GCS scores predicted lower log mean K values, F(1,391)=3.576 (or t=-1.891), p=.06.

## Diagnostics
```{r}
outlierTest(lm_mcq.gcf)
```


# COVID DoG and MCQ
Hypothesis:
People who report more discounting on the general DoG measure will delay less on the adopted COVID 19 specific DoG Task

## Plots
```{r}
hist(dt$logMeanK)
hist(log(dt$COVID_DoG_index))

plot(dt$logMeanK,log(dt$COVID_DoG_index))
```
Maybe a trending negative relationship?

## Stats
```{r}
lm_mcq.cdog<-lm(log(COVID_DoG_index)~logMeanK,data=dt)
summary(lm_mcq.cdog)

#plot
ggplot(aes(x=logMeanK,y=log(COVID_DoG_index)),data=dt)+
  geom_point()+
  geom_smooth(method="lm")
```
A significant negative relationship: higher log mean K values predict lower log COVID DoG indices, F(1,391) = 5.186 (or t=-2.277), p=.023.

## Diagnostics
```{r}
plot(lm_mcq.cdog)

outlierTest(lm_mcq.cdog)

```
3 potential outliers. Let's try without them. 

## w/o outliers
```{r}
#tag outliers in dt
lm_mcq.cdog_outls<-outlierTest(lm_mcq.cdog)$r %>% names() # get list of outlier names
dt$lm_mcq.cdog_out<-ifelse(rownames(dt) %in% lm_mcq.cdog_outls, 1, 0) #tag outliers in dt
#dt %>% filter(lm_mcq.cdog_out==1) %>% select(rownames)#check

#view plot w/ outliers tagged
ggplot(aes(x=logMeanK,y=log(COVID_DoG_index),
           group=as.factor(lm_mcq.cdog_out),colour=as.factor(lm_mcq.cdog_out)),
       data=dt)+
  geom_point()

#stats
lm_mcq.cdog_out<-lm(log(COVID_DoG_index)~logMeanK,
                    data=subset(dt,lm_mcq.cdog_out!=1))
summary(lm_mcq.cdog_out)
```
Removing 3 outliers made results more significant.

# COVID DoG and political orientation
Hypothesis:
Individuals will vary systematically in COVID DoG and norms by political orientation. 
Specifically, Conservatives will delay less than Liberals on the COVID19 DoG task. 

## Plots
```{r}
hist(log(dt$COVID_DoG_index))

#norms
hist(dt$FamilyNorm_index)
hist(dt$FriendsNorm_index)
hist(dt$StrangerNorm_index)

#politics
hist(dt$Measure2_liberal_Index) 
hist(dt$Measure2_cons_Index)
hist(dt$Measure2_liberterian_Index)
hist(dt$Measure5_Political_Index)
hist(dt$Measure5_SECS_Index)
hist(dt$Measure5_Social_Index)
```

### Political orientation
```{r}
#are there separable dimensions of politics here?
#look at a correlation plot
dt_corrs<-subset(dt,select=c(Measure2_liberal_Index,
                             Measure2_cons_Index,
                             Measure2_liberterian_Index,
                             Measure5_Political_Index,
                             Measure5_SECS_Index,
                             Measure5_Social_Index))
chart.Correlation(dt_corrs)
```


## Stats
Do Conservatives will delay less than Liberals on the COVID19 DoG task?
```{r}

```

